% !TEX root =  CurvedFoldedDogs.tex
We present a computational framework 
%set of computational tools 
for 
%unhindered 
interactive design and 
exploration of curved folded sculptures \OSH{sculptures? too pompous. I'd say ``developable shapes/structures/surfaces containing creases and curved folds''}.
%
\OSH{Now what's missing is a sentence of how so far there has been no work allowing such interactive design / why it is hard / why is it a hard and important challenge.}
%
We base our approach on modeling the shapes using discrete orthogonal geodesic nets (DOGs) in a piecewise manner. DOGs are used to represent the smooth parts of the modeled shape, and we connect different DOGs along curves that represent the sharp creases and folds. 
%, based on piecewise discrete orthogonal geodesic nets (DOGs). 
Our main 
%apparatus 
contribution is a discrete binary characterization for folds between DOGs, accompanied by an algorithm to simultaneously fold creases and smoothly bend planar sheets. We complement our algorithm with essential building blocks for curved folding deformations: objectives to control dihedral angles and mountain-valley assignments. We apply our machinery in a curved folding editing system, thus building the first tool capable of modeling bending and folding of complicated crease patterns.

% and explore areas previously uncharted by computer simulations such as wallpaper curved folding, as well as dynamically adding, removing, and moving creases along a flattened pattern.